### 2013-07-07 mcmc.tex
bug
moved likelihood sampling rant to later, removed repitition

...You can't sample a likelihood!  You can only sample a posterior
pdf!..
why not?..
Give a sense of the difficulties you get into if you fail here; like
discussion with Sven Kreiss on 2013-02-14...

@@

>>>>

@@

MCMC is used to obtain samples $x_k$ from pdf $p(x)$,
  or a badly normalized all-positive function $f(x)$
  that is different from the pdf by an unknown factor $Z$.
In the context of data analysis,
  MCMC is usually being used to obtain samples
  that are \emph{parameter values} for a probabilistic model of some data.
That is, MCMC is sampling a pdf \emph{for the parameters}.
If it is returning parameter values, then it is not sampling a pdf for the data.
That is, MCMC can only sample a posterior (or prior) pdf for the parameters.
\emph{It cannot sample a likelihood.}%
\note{Well, technically, MCMC \emph{can} be used to sample a likelihood function,
  but the samples would be samples of possible \emph{data} not possible \emph{parameters}.
  The purist might say that even this is not sampling a likelihood function,
  because you should only call it a ``likelihood function'' in contexts in which you are
  treating the data as fixed (at the true data values) and the parameters as variable.}

Despite all this, in many cases,
  data analysts believe they are sampling the likelihood.
This is because (we presume) they have put a likeilihood function
  (or log-likelihood function)
  in as the input to the MCMC code, where the probability function
  (or log-probability function) should go.
Then is it the likelihood that is being sampled?
No, not really;
it is a posterior probability that is directly proportional to the likelihood function.
That is, it is a posterior probability for some implicit (and improper) ``flat'' priors.

...Give a sense of the difficulties you get into if you fail here; like
discussion with Sven Kreiss on 2013-02-14...

...Explain how your code \emph{should look} with a prior function and a likelihood function...
